Growth trajectories: how functional traits influence plant growth

### 2016-09-16 ms/ms-supp.Rnw
Towards a full draft

\titleprefix{Supporting information for:}

@@

\begin{figure}[ht]
\centering
\includegraphics{SI/growth_light_dia.pdf}
\caption{\textbf{Traits moderate the responsiveness of growth to changes
in light environment (diameter growth).} Panels show predicted relationship between
specific trait and diameter growth rate, for a plant of specified
diameter and under a range of shading environments.
\label{fig:growth_light_dia}}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics{SI/lma_effects_at_diameters.pdf}
\caption{\textbf{The expected correlation between leaf-mass per unit leaf area
and growth rate changes with plant size.} \label{f-lma_growth_size}}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics{SI/lma_effects_at_diameters_relative.pdf}
\caption{\textbf{The expected correlation between leaf-mass per unit leaf area
and relative growth rate changes with plant size.}
\label{f-lma_growth_size_relative}}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics{SI/rho_effects_at_diameters.pdf}
\caption{\textbf{The expected correlation between wood density
and growth rate changes with plant size.} \label{f-rho_growth_size}}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics{SI/rho_effects_at_diameters_relative.pdf}
\caption{\textbf{The expected correlation between wood density
and relative growth rate changes with plant size.}
\label{f-rho_growth_size_relative}}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics{SI/hmat_effects_at_diameters.pdf}
\caption{\textbf{The expected correlation between maximum height and
growth rate changes with plant size.} \label{f-hmat_growth_size}}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics{SI/hmat_effects_at_diameters_relative.pdf}
\caption{\textbf{The expected correlation between maximum height and
relative growth rate changes with plant size.}
\label{f-hmat_growth_size_relative}}
\end{figure}

>>>>

\titleprefix{Supporting Materials for:}

@@

\begin{figure}[ht]
\centering
\includegraphics{SI/growth_light_dia.pdf}
\caption{\textbf{Traits moderate the responsiveness of growth to changes
in light environment (stem-diameter growth).} Panels show predicted relationship between specific trait and diameter growth rate, for a plant of specified
diameter and under a range of shading environments.
\label{fig:growth_light_dia}}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics{SI/growth_light_area.pdf}
\caption{\textbf{Traits moderate the responsiveness of growth to changes
in light environment (stem-area growth).} Panels show predicted relationship between specific trait and diameter growth rate, for a plant of specified
diameter and under a range of shading environments.
\label{fig:growth_light_area}}
\end{figure}

@@
